---
title: "model"
author: "Edmundo Peralta"
date: "23/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidymodels)
library(gt)
library(tidyverse)
library(skimr)
# library(doParallel)
library(ranger)
library(GGally)
library(usemodels)
library(petroreadr)

```

## The Available data

The core samples available in Umm lulu were joined with the log data. A selection of logs was made considering the ones available in most wells.

```{r echo=FALSE, message=FALSE, warning=FALSE}

core_data <- read_rds("../../clean_data/all_logs_for_model.rds") %>% drop_na(SRT_OPCO) %>% 
  select(-c(CoreDesc_Lithofacies_OMV, CoreDesc_Texture_OMV, TVDSS_F,XPEF, XSW,XRHOB,XNPHI,XDT)) %>%
  filter(main_zone != "Dense",main_zone != "HAWAR",
         XPHIT >= 0) %>% 
  mutate(XPERM = XPERM + 0.00001,
         log_XPERM = log10(XPERM),
         log_XDRES = log10(XDRES),
         log_XSRES = log10(XSRES),
         res_diff_lin = XDRES - XSRES,
         res_diff_log = log_XDRES - log_XSRES
         )
  


summary(core_data)

```




## property analysis


```{r fig.width=14}

# core_data %>%     
#     select(-c( MD,Well,RT_all, 
#               `conditions experiment`,
#               estim_perm, 
#               Depth,
#               Zone,
#               SRT_OPCO, zones, 
#               ))%>%
#   mutate(srt = factor(srt)) %>% 
#   ggpairs(aes(colour = srt))

```





### SRT distributions by zone

The following figure shows the available core samples by the 2 main zones:

-   **Kharaib** , including all Kharaib zones excluding the denses
-   **Lekhwair**, including all Lekhwair zones excluding denses.



```{r }
core_data_clean <- 
    core_data %>% 
  rename("srt" = "SRT_OPCO",
         "MD" = "DEPT",
         "Well" = "WELL") %>% 
  mutate(srt = as_factor(srt))

all_logs<-
    core_data_clean 

all_logs %>% 
        ggplot(aes(srt))+
        geom_bar(fill = "darkgreen", alpha = 0.5)+
        facet_wrap(vars(main_zone),
                   scales = "free")+
        coord_flip()+
        theme_bw()+
        labs(x = "SRT",
             y= "Core samples")



```



Given the distribution of SRTs, we will use a stratified methodology for sampling the dataset to mini ize the effect of the imbalance in the data sampling.


### traning the Kharaib




```{r}

logs <- c("XGR", "XDRES", "XPHIT", "XPERM", "res_diff_lin")


to_train <-
  all_logs %>% 
    select(logs, srt, MD, Well, main_zone) %>% 
    drop_na()


    xdata <-
      to_train %>% 
      select(logs,  
             MD,Well, srt,main_zone
             )
    

    
    
    
    kh_split <- xdata %>% 
      filter(main_zone == "Kharaib") %>%   
      initial_split( ) #, strata = status_id)
    

    kh_train <- training(kh_split)

    
     rf_spec <- rand_forest(trees = 1000) %>% 
        set_mode("classification") %>% 
        set_engine("ranger")
    
    
    kh_recipe <- 
      recipe(formula = srt ~ . , data =  kh_train) %>% 
      update_role(MD , new_role = "id") %>% 
      update_role(Well , new_role = "id") %>% 
      update_role(main_zone , new_role = "id") 
    
   kh_wf <- workflow() %>% 
        add_recipe(kh_recipe) %>% 
        add_model(rf_spec)  
    
    
    
set.seed(123)

  kh_fit <- fit(kh_wf, kh_train)

  
  
  
  
  
  
```
## load the logs to model




```{r}


xdata <- read_rds("../../clean_data/all_logs_for_model.rds") %>% 
  rename("MD" = "DEPT",
         "Well" = "WELL", 
         ) %>%
  select("XGR", "XDRES", "XPHIT", "XPERM", "res_diff_lin","MD", "Well", "main_zone") %>% 
  drop_na()

kharaib_rrt<- predict(kh_fit, xdata)


temp_df <- xdata %>% 
  add_column(kharaib_rrt) %>% 
  mutate(srt_kh = if_else(.pred_class == "1", 1, 0),
         srt_kh = if_else(.pred_class == "2", 2, srt_kh),
         srt_kh = if_else(.pred_class == "3", 3, srt_kh),
         srt_kh = if_else(.pred_class == "4", 4, srt_kh),
         srt_kh = if_else(.pred_class == "5", 5, srt_kh),
         srt_kh = if_else(.pred_class == "6", 6, srt_kh),
         ) %>% 
  select(Well, MD, srt_kh) %>% 
  rename(DEPT = MD, 
         WELL = Well) %>% 
  group_by(WELL) %>% 
  do(write_las0(., name = unique(.$WELL), do = TRUE))
  
rm(temp_df)


```


## lekhwair


```{r}

logs <- c( "XGR", "XPHIT", "res_diff_log", "log_XPERM", "log_XDRES" )
 

to_train <-
  all_logs %>% 
    select(logs, srt, MD, Well, main_zone) %>% 
    drop_na()


    xdata <-
      to_train %>% 
      select(logs,  
             MD,Well, srt,main_zone
             )
    

    
    

    lk_split <- xdata %>% 
      filter(main_zone == "Lekhwair") %>%   
      initial_split( ) #, strata = status_id)
    

    lk_train <- training(lk_split)
    

    lk_test <- testing(lk_split)
   
        
    rf_spec <- rand_forest(trees = 1000) %>% 
        set_mode("classification") %>% 
        set_engine("ranger")
    
    
    lk_recipe <- 
      recipe(formula = srt ~ . , data =  lk_train) %>% 
      update_role(MD , new_role = "id") %>% 
      update_role(Well , new_role = "id") %>% 
      update_role(main_zone , new_role = "id") 
    

    
    lk_wf <- workflow() %>% 
        add_recipe(lk_recipe) %>% 
        add_model(rf_spec) 

  lk_fit <- fit(lk_wf, lk_train)
  
  
  
  
```


## Predicton
```{r}


xdata <- read_rds("../../clean_data/all_logs_for_model.rds") %>% 
  rename(MD = DEPT,
         Well = WELL, 
         ) %>%
  select("XGR", "XPHIT", "res_diff_log", "log_XPERM", "log_XDRES" , "main_zone" , "Well", "MD" ) %>% 
  drop_na()

lekhwair_rrt<- predict(lk_fit, xdata)

temp_df <- xdata %>% 
  add_column(lekhwair_rrt) %>% 
  mutate(srt_lkh = if_else(.pred_class == "1", 1, 0),
         srt_lkh = if_else(.pred_class == "2", 2, srt_lkh),
         srt_lkh = if_else(.pred_class == "3", 3, srt_lkh),
         srt_lkh = if_else(.pred_class == "4", 4, srt_lkh),
         srt_lkh = if_else(.pred_class == "5", 5, srt_lkh),
         srt_lkh = if_else(.pred_class == "6", 6, srt_lkh),
         ) %>% 
  select(Well, MD, srt_lkh) %>% 
  rename(DEPT = MD, 
         WELL = Well) %>% 
  group_by(WELL) %>% 
  do(write_las0(., name = unique(.$WELL), do = TRUE))
  
rm(temp_df)




```



