---
title: "model excluding logs not common to most wells"
author: "Edmundo Peralta"
date: "18/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidymodels)
library(gt)
library(tidymodels)
library(skimr)
library(doParallel)
library(ranger)
library(GGally)
library(usemodels)

```

## The Available data

The core samples available in Umm lulu were joined with the log data. A selection of logs was made considering the ones available in most wells.

```{r echo=FALSE, message=FALSE, warning=FALSE}

core_data <- readRDS("../../clean_data/core_ready.rds") %>% 
       mutate(main_zone = ifelse(Zone < 10 , "Kharaib"    , "other" ),
           main_zone = ifelse(Zone == 4 ,  "Dense"     , main_zone ),
           main_zone = ifelse(Zone == 6 ,  "Dense"     , main_zone ),
           main_zone = ifelse(Zone == 10 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone >  10 ,  "Lekhwair" , main_zone ),
           main_zone = ifelse(Zone == 12 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 16 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 16 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 20 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 22 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 24 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 26 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 28 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 29 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 30 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 32 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 34 ,  "Dense"    , main_zone ),
           main_zone = as.factor(main_zone)
                      )


head(core_data) %>% 
    select(-c(RT_all, 
              `conditions experiment`,
              estim_perm, 
              Depth,
              Zone,
              SRT_OPCO,
              XPEF,
              XDT,
              XNPHI,
              XRHOB,
              XSW))%>% 
    gt() %>% 
    fmt_number(columns = c(poro,  XDRES,XSRES,XPHIT),
               decimals = 2
               ) %>% 
    fmt_number(columns = c(perm, XPERM),
               decimals = 1
               ) %>% 
    cols_move_to_start(Well) %>% 
    cols_width(
        starts_with("sr") ~ px(1000)
        
        ) %>% 
    tab_header(
        title = md("Subset of **Core data** with associated well log values")
    )

```

### Main statistics of the available dataset

The following table shows the main statistics of the data set.

```{r echo=FALSE, message=FALSE, warning=FALSE}
core_data %>%     
    select(-c(RT_all, 
              `conditions experiment`,
              estim_perm, 
              Depth,
              Zone,
              SRT_OPCO,
              XPEF,
              XDT,
              XNPHI,
              XRHOB,
              XSW
              ))%>%
    # group_by(Well) %>% 
    skim()


```


## property analysis


```{r fig.width=14}

# core_data %>%     
#     select(-c( MD,Well,RT_all, 
#               `conditions experiment`,
#               estim_perm, 
#               Depth,
#               Zone,
#               SRT_OPCO, zones, 
#               ))%>%
#   mutate(srt = factor(srt)) %>% 
#   ggpairs(aes(colour = srt))

```





### SRT distributions by zone

The following figure shows the available core samples by the 2 main zones:

-   **Kharaib** , including all Kharaib zones excluding the denses
-   **Lekhwair**, including all Lekhwair zones excluding denses.



```{r }
core_data_clean <- 
    core_data %>% 
        filter(main_zone != "Dense",
               XPHIT >= 0) %>% 
    select(-c(XDT,XPEF,XSW, estim_perm  ,
              XDT,
              XNPHI,
              XRHOB
              ))

all_logs<-
    core_data_clean %>% 
    select(-c(Depth, 
              poro,
              perm,
              `conditions experiment`, 
              RT_all, 
              SRT_OPCO, 
              Zone,
              zones))

all_logs %>% 
        ggplot(aes(srt))+
        geom_bar(fill = "darkgreen", alpha = 0.5)+
        facet_wrap(vars(main_zone),
                   scales = "free")+
        coord_flip()+
        theme_bw()+
        labs(x = "SRT",
             y= "Core samples")



```



Given the distribution of SRTs, we will use a stratified methodology for sampling the dataset to mini ize the effect of the imbalance in the data sampling.



## Data preparation


### create logarithmic logs

We create the logs, and add 0.00001md to XPERM to eliminate the problem with the 0 and the logarithm going to inf. (see the stats above were the minimum value in perm is 0)


```{r}

all_logs <- all_logs %>% 
  mutate(XPERM = XPERM + 0.00001,
         log_XPERM = log10(XPERM),
         log_XDRES = log10(XDRES),
         log_XSRES = log10(XSRES),
         res_diff_lin = XDRES - XSRES,
         res_diff_log = log_XDRES - log_XSRES
         )

summary(all_logs)
```

 step_zv(all_predictors())
  update_role(row_id, new_role = "id") %>%
   step_other(all_nominal_predictors(), threshold = 0.03) %>%
     step_impute_linear(install_year) %>%
  step_downsample(status_id)
### traning and split


```{r}
#usemodels::use_ranger(srt ~ . , kh_train )
```





```{r}

set.seed(123)


## variables to run the loops


      kh_roc_auc_max <-0
      lk_roc_auc_max <-0
      r2_max <- 1e22
      r2_max_v2 <-0
      perm <- 0
      perm_max <- 0
      perm_max_v2 <- 0
      perm_max_v3 <- 0
      count <-0
      
      
## selection of curves to run the model      

logs <- c("XGR", "XDRES", "XSRES", "XPHIT", "XPERM", "res_diff_log", "res_diff_lin", "log_XPERM", "log_XDRES", "log_XSRES")

to_train <-
  all_logs %>% 
    select(logs, srt, MD, Well, main_zone) %>% 
    drop_na()


### número máximo de logs
n<- length(logs)

for (i in 8:n) {
  temp <- combn(logs,i)
  
  loop <- ncol(temp)
  
  for (j in 1:loop) {
    
    print(paste0("van ", count, " runs"))
    
    logs_to_run <- temp[,j]
    
    xdata <-
      to_train %>% 
      select(logs_to_run,  
             MD,Well, srt,main_zone
             )
    
    kh_split <- xdata %>% 
      filter(main_zone == "Kharaib") %>%   
      initial_split( ) #, strata = status_id)
    
    lk_split <- xdata %>% 
      filter(main_zone == "Lekhwair") %>%   
      initial_split( ) #, strata = status_id)
    
    kh_train <- training(kh_split)
    lk_train <- training(lk_split)
    
    kh_test <- testing(kh_split)
    lk_test <- testing(lk_split)
    
    
    core_folds_kh <- kh_train %>%
      # filter(main_zone == "Kharaib") %>% 
      #   select(-c(MD, Well, main_zone )) %>% 
        mutate(srt = factor(srt)) %>% 
        bootstraps(
          # strata = srt
          )
    
    core_folds_lk <- lk_train %>%
      # filter(main_zone == "Lekhwair") %>% 
      #   select(-c(MD,Well, main_zone )) %>% 
        mutate(srt = factor(srt)) %>% 
        bootstraps(
          # strata = srt
          )
    
    rf_spec <- rand_forest(trees = 1000) %>% 
        set_mode("classification") %>% 
        set_engine("ranger")
    
    
    kh_recipe <- 
      recipe(formula = srt ~ . , data =  kh_train) %>% 
      update_role(MD , new_role = "id") %>% 
      update_role(Well , new_role = "id") %>% 
      update_role(main_zone , new_role = "id") 
    
    lk_recipe <- 
      recipe(formula = srt ~ . , data =  lk_train) %>% 
      update_role(MD , new_role = "id") %>% 
      update_role(Well , new_role = "id") %>% 
      update_role(main_zone , new_role = "id") 
    
    
    kh_wf <- workflow() %>% 
        add_recipe(kh_recipe) %>% 
        add_model(rf_spec)
    
    lk_wf <- workflow() %>% 
        add_recipe(lk_recipe) %>% 
        add_model(rf_spec)
    
    
    no_cores <- detectCores() - 1 
     doParallel::registerDoParallel(cores = no_cores)
    kh_rs <- fit_resamples(
      kh_wf,
      resamples = core_folds_kh,
      control = control_resamples(save_pred = TRUE)
    )
    

      
     doParallel::registerDoParallel(cores = no_cores)
    lk_rs <- fit_resamples(
      lk_wf,
      resamples = core_folds_lk,
      control = control_resamples(save_pred = TRUE)
    )
    
  
    
    metric_kh <- collect_metrics(kh_rs)    
    metric_lk <- collect_metrics(lk_rs)   
    
    kh_roc_auc <-  metric_kh[["mean"]][2]
    lk_roc_auc <-  metric_lk[["mean"]][2]
    
    count <- count +1    
    if (kh_roc_auc > kh_roc_auc_max) {
      
      kh_the_logs <- logs_to_run
      
      kh_roc_auc_max <- kh_roc_auc
      
      print(cat( count ,  kh_roc_auc_max, kh_the_logs))
      
      # kh_fit <- fit(kh_wf, kh_train)
      
      
    }
    
       count <- count +1 
        
    if (lk_roc_auc > lk_roc_auc_max) {
      
      lk_the_logs <- logs_to_run
      
      lk_roc_auc_max <- lk_roc_auc
      
      print(cat( count ,  lk_roc_auc_max, lk_the_logs))
      
      # lk_fit <- fit(lk_wf, lk_train)
      
      
    }
    

    
    
    
  }

}





```


```{r}

logs <- c("XGR"    ,   "XRHOB"   ,  "XPHIT"  ,   "log_XPERM" ,"log_XDRES", "log_XSRES")


to_train <-
  all_logs %>% 
    select(logs, srt, MD, Well, main_zone) %>% 
    drop_na()


    xdata <-
      to_train %>% 
      select(logs,  
             MD,Well, srt,main_zone
             )
    

    
    
    
    kh_split <- xdata %>% 
      filter(main_zone == "Kharaib") %>%   
      initial_split( ) #, strata = status_id)
    

    kh_train <- training(kh_split)

    
     rf_spec <- rand_forest(trees = 1000) %>% 
        set_mode("classification") %>% 
        set_engine("ranger")
    
    
    kh_recipe <- 
      recipe(formula = srt ~ . , data =  kh_train) %>% 
      update_role(MD , new_role = "id") %>% 
      update_role(Well , new_role = "id") %>% 
      update_role(main_zone , new_role = "id") 
    
   kh_wf <- workflow() %>% 
        add_recipe(kh_recipe) %>% 
        add_model(rf_spec)  
    
    
    
set.seed(123)

  kh_fit <- fit(kh_wf, kh_train)

  
  
  
  
  
  
```
## load the logs to model




```{r}
xdata <- read_rds("../../clean_data/all_logs_for_model.rds") %>% 
  rename(MD = DEPT,
         Well = WELL, 
         ) %>%
  select("XGR"    ,   "XRHOB"   ,  "XPHIT"  ,   "log_XPERM" ,"log_XDRES", "log_XSRES", "main_zone" , "Well", "MD" ) %>% 
  drop_na()

kharaib_rrt<- predict(kh_fit, xdata)


```





```{r}

logs <- c("XGR"   ,       "XSRES"    ,    "XRHOB"   ,     "XPHIT",        "res_diff_log" ,"res_diff_lin", "log_XPERM"  )


to_train <-
  all_logs %>% 
    select(logs, srt, MD, Well, main_zone) %>% 
    drop_na()


    xdata <-
      to_train %>% 
      select(logs,  
             MD,Well, srt,main_zone
             )
    

    
    

    lk_split <- xdata %>% 
      filter(main_zone == "Lekhwair") %>%   
      initial_split( ) #, strata = status_id)
    

    lk_train <- training(lk_split)
    

    lk_test <- testing(lk_split)
   
        
    rf_spec <- rand_forest(trees = 1000) %>% 
        set_mode("classification") %>% 
        set_engine("ranger")
    
    
    lk_recipe <- 
      recipe(formula = srt ~ . , data =  lk_train) %>% 
      update_role(MD , new_role = "id") %>% 
      update_role(Well , new_role = "id") %>% 
      update_role(main_zone , new_role = "id") 
    

    
    lk_wf <- workflow() %>% 
        add_recipe(lk_recipe) %>% 
        add_model(rf_spec) 

  lk_fit <- fit(lk_wf, lk_train)
  
  
  
  
```


## Predicton
```{r}


xdata <- read_rds("../../clean_data/all_logs_for_model.rds") %>% 
  rename(MD = DEPT,
         Well = WELL, 
         ) %>%
  select("XGR"   ,       "XSRES"    ,    "XRHOB"   ,     "XPHIT",        "res_diff_log" ,"res_diff_lin", "log_XPERM" , "main_zone" , "Well", "MD" ) %>% 
  drop_na()

lekhwair_rrt<- predict(lk_fit, xdata)




```




bird_fit <- fit(wf_interact, bird_train)

predict(bird_fit, bird_test, type = "prob")


```{r}


rf_spec <- rand_forest(trees = 1000) %>% 
    set_mode("classification") %>% 
    set_engine("ranger")


core_wf <- workflow() %>% 
    add_formula(srt ~ .) %>% 
    add_model(rf_spec)

core_wf
    


doParallel::registerDoParallel()
core_rs <- fit_resamples(
  core_wf,
  resamples = core_folds,
  control = control_resamples(save_pred = TRUE)
)
core_rs



```

Lets fit the random forest model to the bootstrap resamples

```{r}

doParallel::registerDoParallel()
core_rs <- fit_resamples(
  core_wf,
  resamples = core_folds,
  control = control_resamples(save_pred = TRUE)
)
core_rs

```

## Evaluate the metrics

```{r}

collect_metrics(core_rs)

```



```{r}
core_rs %>%
  collect_predictions() %>%
  group_by(id) %>%
  ppv(srt, .pred_class)
```


```{r}
core_rs %>%
  collect_predictions() %>%
  group_by(id) %>%
  roc_curve(srt, `.pred_SRT-1`:`.pred_SRT-6`) %>%
  ggplot(aes(1 - specificity, sensitivity, color = id)) +
  geom_abline(lty = 2, color = "gray80", size = 1.5) +
  geom_path(show.legend = FALSE, alpha = 0.6, size = 1.2) +
  facet_wrap(~.level, ncol = 3) +
  coord_equal()+
  theme_minimal()
```


