---
title: "model"
author: "Edmundo Peralta"
date: "18/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidymodels)
library(gt)
library(tidymodels)
library(skimr)
library(doParallel)
library(ranger)
library(GGally)

```

## The Available data

The core samples available in Umm lulu were joined with the log data. A selection of logs was made considering the ones available in most wells.

```{r echo=FALSE, message=FALSE, warning=FALSE}

core_data <- readRDS("../../clean_data/core_ready.rds") %>% 
       mutate(main_zone = ifelse(Zone < 10 , "Kharaib"    , "other" ),
           main_zone = ifelse(Zone == 4 ,  "Dense"     , main_zone ),
           main_zone = ifelse(Zone == 6 ,  "Dense"     , main_zone ),
           main_zone = ifelse(Zone == 10 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone >  10 ,  "Lekhwair" , main_zone ),
           main_zone = ifelse(Zone == 12 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 16 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 16 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 20 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 22 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 24 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 26 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 28 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 29 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 30 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 32 ,  "Dense"    , main_zone ),
           main_zone = ifelse(Zone == 34 ,  "Dense"    , main_zone ),
           main_zone = as.factor(main_zone)
                      )


head(core_data) %>% 
    select(-c(RT_all, 
              `conditions experiment`,
              estim_perm, 
              Depth,
              Zone,
              SRT_OPCO))%>% 
    gt() %>% 
    fmt_number(columns = c(poro, XNPHI,XRHOB,XSW, XDRES,XSRES,XPEF,XPHIT),
               decimals = 2
               ) %>% 
    fmt_number(columns = c(perm, XPERM),
               decimals = 1
               ) %>% 
    cols_move_to_start(Well) %>% 
    cols_width(
        starts_with("sr") ~ px(1000)
        
        ) %>% 
    tab_header(
        title = md("Subset of **Core data** with associated well log values")
    )

```

### Main statistics of the available dataset

The following table shows the main statistics of the data set.

```{r echo=FALSE, message=FALSE, warning=FALSE}
core_data %>%     
    select(-c(RT_all, 
              `conditions experiment`,
              estim_perm, 
              Depth,
              Zone,
              SRT_OPCO
              ))%>%
    # group_by(Well) %>% 
    skim()


```


## property analysis


```{r fig.width=14}

core_data %>%     
    select(-c( MD,Well,RT_all, 
              `conditions experiment`,
              estim_perm, 
              Depth,
              Zone,
              SRT_OPCO, zones, 
              ))%>%
  mutate(srt = factor(srt)) %>% 
  ggpairs(aes(colour = srt))

```





### SRT distributions by zone

The following figure shows the available core samples by the 2 main zones:

-   **Kharaib** , including all Kharaib zones excluding the denses
-   **Lekhwair**, including all Lekhwair zones excluding denses.



```{r }
core_data_clean <- 
    core_data %>% 
        filter(main_zone != "Dense",
               XPHIT >= 0) %>% 
    select(-c(XDT,XPEF,XSW, estim_perm))

to_train<-
    core_data_clean %>% 
    select(-c(Depth, poro,perm, `conditions experiment`, RT_all, SRT_OPCO))

to_train %>% 
        ggplot(aes(srt))+
        geom_bar(fill = "darkgreen", alpha = 0.5)+
        facet_wrap(vars(main_zone),
                   scales = "free")+
        coord_flip()+
        theme_bw()+
        labs(x = "SRT",
             y= "Core samples")



```



Given the distribution of SRTs, we will use a stratified methodology for sampling the dataset to mini ize the effect of the imbalance in the data sampling.



## Data prepareation

### traning and split


```{r echo=FALSE, message=FALSE, warning=FALSE}


set.seed(123)
core_folds <- to_train %>%
  filter(main_zone == "Kharaib") %>% 
    select(-c(MD, Well,Zone, zones, main_zone )) %>% 
    mutate(srt = factor(srt)) %>% 
    bootstraps(
      # strata = srt
      )

core_folds

```


```{r}

rf_spec <- rand_forest(trees = 1000) %>% 
    set_mode("classification") %>% 
    set_engine("ranger")


core_wf <- workflow() %>% 
    add_formula(srt ~ .) %>% 
    add_model(rf_spec)

core_wf
    





```

Lets fit the random forest model to the bootstrap resamples

```{r}

doParallel::registerDoParallel()
core_rs <- fit_resamples(
  core_wf,
  resamples = core_folds,
  control = control_resamples(save_pred = TRUE)
)
core_rs

```

## Evaluate the metrics

```{r}

collect_metrics(core_rs)

```



```{r}
core_rs %>%
  collect_predictions() %>%
  group_by(id) %>%
  ppv(srt, .pred_class)
```


```{r}
core_rs %>%
  collect_predictions() %>%
  group_by(id) %>%
  roc_curve(srt, `.pred_SRT-1`:`.pred_SRT-6`) %>%
  ggplot(aes(1 - specificity, sensitivity, color = id)) +
  geom_abline(lty = 2, color = "gray80", size = 1.5) +
  geom_path(show.legend = FALSE, alpha = 0.6, size = 1.2) +
  facet_wrap(~.level, ncol = 3) +
  coord_equal()+
  theme_minimal()
```


